The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-04 manuscript.Rmd
edit  barcoding results

The marine invertebrates of the US have generally been characterized genetically at a higher level than other parts of the world: `r format_output(prop_spp_barcoded$p_barcoded * 100)`% (n = `r format(nrow(combined_species), big.mark=",")`) of the fauna has DNA barcodes available.  In 2012, it was estimated that, at a global scale, less than 3% of the marine species had been sequenced [@Appeltans2012], and that this number was even lower in some areas (e.g., 2.6% for the Antarctic [@Grant2009]).  This proportion varies by phylum from `r format_output(stat_barcoding$min_eez_value * 100)`% for `r stat_barcoding$min_eez_phylum` to `r format_output(stat_barcoding$max_eez_value * 100)`% for `r stat_barcoding$max_eez_phylum` (Fig. \@ref(fig:proportion-barcoded)). The GOM has comparable coverage in level of DNA barcoding of the fauna to the EEZ, while the PNW is better barcoded with >30% species-level coverage across each of the five most diverse phyla. This is driven in part by the active Canadian barcoding effort in British Columbia.

The above estimates are based on species names, but many traditional species include multiple cryptic species [@Knowlton2000;@Meyer2005-evolution]. For example, up to `r format_output(100 * stat_bold$p_spp_multi_bin)`% of `r format(stat_bold$n_spp_not_singleton, big.mark=",")` species represented by more than 1 record in BOLD include cryptic species, as denoted by assignment to  more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]). Specimens identified under the same species but sampled from distant locations, are especially prone to representing cryptic species. Geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records, big.mark=",")` BOLD records analyzed here have no geographic coordinate information associated with them). It is thus crucial to ensure that precise and accurate geographic information is provided when DNA barcodes are published, and that enough samples for each species are sequenced, to capture more accurately their geographic range and the extent of their genetic diversity.

>>>>

The marine invertebrates of the US have generally been characterized genetically at a higher level than other parts of the world: `r format_output(prop_spp_barcoded$p_barcoded * 100)`% (n = `r format(nrow(combined_species), big.mark=",")`) of the digitized fauna has DNA barcodes available.  In 2012, it was estimated that, at a global scale, less than 3% of the marine species had been sequenced [@Appeltans2012], and that this number was even lower in some areas (e.g., 2.6% for the Antarctic [@Grant2009]).  This proportion varies by phylum from `r format_output(stat_barcoding$min_eez_value * 100)`% for `r stat_barcoding$min_eez_phylum` to `r format_output(stat_barcoding$max_eez_value * 100)`% for `r stat_barcoding$max_eez_phylum` (Fig. \@ref(fig:proportion-barcoded)). The GOM has comparable coverage in level of DNA barcoding of the fauna to the EEZ, while the PNW is better barcoded with >30% species-level coverage across each of the five most diverse phyla. This is driven in part by the active Canadian barcoding effort in British Columbia.

The above estimates are based on species names, but many traditional species include multiple cryptic species [@Knowlton2000;@Meyer2005-evolution]. For example, up to `r format_output(100 * stat_bold$p_spp_multi_bin)`% of `r format(stat_bold$n_spp_not_singleton, big.mark=",")` species represented by more than 1 record in BOLD include cryptic species, as denoted by assignment to  more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]). Specimens identified under the same species but sampled from distant locations are especially prone to representing cryptic species. While geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records, big.mark=",")` BOLD records analyzed here have no geographic coordinate information associated with them), of the `r bold_geography_stats$n_spp_with_records` marine invertebrates species from the US with BOLD records, only `r format_output(bold_geography_stats$p_within_eez * 100)`% have at least one record collected within the EEZ, and `r format_output(bold_geography_stats$p_in_north_america * 100)`% list a North American country as the site of collection. Although DNA barcodes are available for `r format_output(prop_spp_barcoded$p_barcoded * 100)`% of the marine invertebrate fauna, many of these records have been collected outside the Atlantic and Pacific US biogeographic regions, and therefore geographical differentiation has not been evaluated for most taxa. It is thus crucial to ensure that precise and accurate geographic information is provided when DNA barcodes are published, and that enough samples for each species are sequenced to capture more accurately their geographic range and the extent of their genetic diversity.
